### 2015-02-04 paper_10_intro.tex
increased image size
adding info about 3 focus areas and 3 questions

\subsubsection{SOFTWARE ANALYTICS}

@@

    The goal of software analytics is to extract insights
    from software artifacts to aide practitioners in making 
    better decisions regarding software
    development \cite{Zhang2013}.  The three main focus areas of 
    software analytics are:
    \begin{description}
        \item[User Experience] - How can the software enable the 
            user to more easily or quickly 
            accomplish the task at hand?
        \item[Quality] - How can the number of problems with 
            the software be decreased?
        \item[Development Productivity] - How can the processes
            or tools be modified to increase 
            the rate at which software is produced? 
    \end{description}
    The work presented later in this paper will address all three
    focus areas.

    Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
    analytics must address:
    \begin{enumerate}
        \item ``How much better is my model performing than 
            a naive strategy, such as guessing [\ldots]?''
        \item ``How practically significant are the results?''
        \item ``How sensitive are the results to small changes in 
            one or more of the inputs?''
    \end{enumerate}
    These are 3 important questions that should be addressed 
    when presenting any results in software analytics.  The research
    needs to demonstrate clear advantages for practitioners.

@@

The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
an overview of software, software development lifecycles, software engineering, and software
development organizations.  Chapter 3 introduces what is meant by the term data-driven
software engineering. Chapter 4 then provides an explanation of the Master Performance 
Indicator (MPI).  It will present the essential elements for calculating the MPI, as well
as the formulas, frameworks, and data necessary to produce the MPI. Chapter 5 provides
a technological framework for generating and storing the current and historical MPI values.
Chapter 6 demostrates how MPI can be implemented in a software development portion of 
a large financial institution.  Chapter 7 concludes the dissertation with a summary
of the results and some possible future directions for further enhancements.

>>>>

\subsubsection{SOFTWARE ANALYTICS}
\label{subsub:softwareanalytics}

@@

    The goal of software analytics is to extract insights
    from software artifacts to aide practitioners in making 
    better decisions regarding software
    development \cite{Zhang2013}.  The three main focus areas of 
    software analytics are:
    \begin{enumerate}
        \item \textbf{User Experience} - How can the software enable the 
            user to more easily or quickly 
            accomplish the task at hand?
        \item \textbf{Quality} - How can the number of problems with 
            the software be decreased?
        \item \textbf{Development Productivity} - How can the processes
            or tools be modified to increase 
            the rate at which software is produced? 
    \end{enumerate}

    Later, Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
    analytics must address:
    \begin{enumerate}
        \item ``How much better is my model performing than 
            a naive strategy, such as guessing [\ldots]?''
        \item ``How practically significant are the results?''
        \item ``How sensitive are the results to small changes in 
            one or more of the inputs?''
    \end{enumerate}
    These are 3 important questions that should be addressed 
    when presenting any results in software analytics.  The research
    needs to demonstrate clear advantages for practitioners.  The work
    presented in this work will address both the 3 main focus areas and
    the 3 important questions of software analytics.

@@

The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
an overview of software, software development lifecycles, software engineering, and software
development organizations.  Chapter 3 introduces what is meant by the term data-driven
software engineering. Chapter 4 then provides an explanation of the Master Performance 
Indicator (MPI).  It will present the essential elements for calculating the MPI, as well
as the formulas, framework, and data necessary to produce the MPI. Chapter 5 provides
a technological framework for generating and storing the current and historical MPI values.
Chapter 6 demostrates how MPI can be implemented in a software development portion of 
a large financial institution.  Chapter 7 concludes the dissertation with a summary
of the results and some possible future directions for further enhancements.

### 2015-02-04 paper_40_mpi.tex
adding some more papers
capitalize some table and image names
updated the PDF output file
adding info about 3 focus areas and 3 questions

\section{ELEMENTS OF MPI}

@@

\caption{Availability - Inputs}
\label{tab:avail}
\end{longtable}

@@

\caption{Quality - Inputs}
\label{tab:quality}
\end{longtable}

@@

\caption{Satisfaction - Inputs}
\label{tab:satisfaction}
\end{longtable}

@@

    \subsubsection{Overview}
        Delivery of software in a timely manner is an essential part of being a 
        successful SDO.  Being able to meet scheduled deadlines is a sign of accurate
        estimation and planning.  Drastically missing deadlines is a sign of an SDO
        with a process that needs refinement.  Studies have shown that 
        software projects exceed the estimates by an average of
        30\% \cite{Jorgensen2014}.  Thus it is important to score SDOs on accurate
        schedule adherence. Without tracking and measuring schedule adherence, it will
        not improve.

@@

\caption{Schedule - Inputs}
\label{tab:sched}
\end{longtable}

@@

\caption{Requirements - Inputs}
\label{tab:req}
\end{longtable}

@@

>>>>

\section{MASTER PERFORMANCE INDICATOR (MPI)}

@@

\caption{AVAILABILITY - INPUTS}
\label{tab:avail}
\end{longtable}

@@

\caption{QUALITY - INPUTS}
\label{tab:quality}
\end{longtable}

@@

\caption{SATISFACTION - INPUTS}
\label{tab:satisfaction}
\end{longtable}

@@

        Delivery of software in a timely manner is an essential part of being a 
        successful SDO.  Being able to meet scheduled deadlines is a sign of accurate
        estimation and planning.  Drastically missing deadlines is a sign of an SDO
        with a process that needs refinement.  Studies have shown that 
        software projects exceed the estimates by an average of
        30\% \cite{Jorgensen2014}.  Thus it is important to score SDOs on accurate
        schedule adherence. Without tracking and measuring schedule adherence, it will
        not improve.

@@

\caption{SCHEDULE - INPUTS}
\label{tab:sched}
\end{longtable}

@@

\caption{REQUIREMENT - INPUTS}
\label{tab:req}
\end{longtable}

@@

\subsection{SENSITIVITY OF MPI}
\label{sub:sensitivity}

For more on sensitivity analysis in statistical modeling, see \cite{Saltelli2000}.

\subsection{IMPORTANCE OF MPI}

Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus areas and 3 important questions for software
analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses
each focus area.  
As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does provide
any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
the focus areas.

\begin{longtable}{p{3cm}p{11cm}}
% pairs: absolute number (percentage)

\toprule%
 \centering%
 {\bfseries Focus Area}
 & {\bfseries Why MPI?} \\

\cmidrule[0.4pt](r{0.125em}){1-1}%
\cmidrule[0.4pt](lr{0.125em}){2-2}%
% \midrule
\endhead

User Experience & One of the 5 elements of MPI is satisfaction.  While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
with the software product. Does it have the correct features? Are new features added in a timely manner? Of course, specific survey questions can be created to focus solely on a certain user experience. \\
\myrowcolour%
Quality & Again, one of the 5 elements specifically focuses on quality.  MPI provides a single number
to measure quality.  Therefore, it is easy to track changes in quality over time.  MPI does not address
how to improve the quality, but without a consistent measurement, it would be impossible to determine the change in quality. \\
Development Productivity & The combination of MPI elements, schedule and requirements, provide an 
indication of development productivity. The schedule element measures the productivity
related to estimated schedule. Similarly, the requirement element measures the amount of
work actually being completed.  \\

\caption{SOFTWARE ANALYTICS FOCUS AREAS AND MPI}
\label{tab:focusareas}
\end{longtable}

\begin{longtable}{p{4cm}p{10cm}}
% pairs: absolute number (percentage)

\toprule%
 \centering%
 {\bfseries Question}
 & {\bfseries Why MPI?} \\

\cmidrule[0.4pt](r{0.125em}){1-1}%
\cmidrule[0.4pt](lr{0.125em}){2-2}%
% \midrule
\endhead

How much better is my model performing than a naive strategy, such as guessing? & MPI 
provides consistency which may not exist without it.  Therefore, MPI removes the 
guesswork of measuring a software development organization. \\
\myrowcolour%
How practically significant are the results? &  \\
How sensitive are the results to small changes in one or more of the inputs? & 
The question was extensively addressed in section \ref{sub:sensitivity}.  It appears MPI is
not overly sensitive to small changes in the inputs.\\

\caption{3 IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
\label{tab:questions}
\end{longtable}

### 2015-02-04 paper_50_sdlc-ae.tex
adding info about 3 focus areas and 3 questions

In order for an SDO to properly track the elements of MPI, a data storage system should be available to store the appropriate data.   This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.

>>>>

In order for an SDO to properly track the elements of MPI, a data storage system should be available to store the appropriate data.  A consistent storage system should help to avoid the problem of inaccurate
data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
is implemented correctly by allowing limited changes to existing data, it will be able to alliviate
some of the dishonesty that is currently present in software projects \cite{Rost2011}. This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.
